### 2019-03-03 docs/notebooks/results.Rmd
rewrite intro in notebooks/results.ipynb + .Rmd

## Introduction
### Visual search tasks for investigating attention
In the "classical" form of the visual search paradigm [@wolfeVisualSearch1998], experimenters present a subject with a search display on which there are discrete items, i.e. objects. The subject is asked to report whether a target is present among distractors. The experimenter sets the probability that the target will be present on any given trial. Experimenters measure the reaction time and/or accuracy of the subjects. Often, the results are presented as a plot of reaction time as a function of set size (the number of discrete items in stimulus). By fitting a line to the plot of reaction times as a function of set size and taking the slope of that line, experimenters produced estimates of processing speed, i.e. "seconds per item". Slopes are almost horizontal when subjects are shown visual search stimuli where targets differ from distractors in some clearly salient **feature**, e.g. a red target among green distractors, and slopes become much steeper when targets differ from distractors in some harder-to-distinguish **spatial conjunction** of features, e.g., a digital 2 among digital 5s. Some examples of these stimuli are shown below, generated with https://github.com/NickleDave/searchstims.

>>>>

## Introduction

### Convolutional neural networks and attentional mechanisms
Neural networks have in the past few years transitioned from being an academic area of artificial intellgience to being powerful tools for engineers working in areas such as image classification, speech-to-text, and automatic translation, to name but a few. In the 1980s, artificial neural networks trained with backpropagation gave rise to [Connectionist](https://en.wikipedia.org/wiki/Connectionism) models of cognition. Similar neural network models lie at the heart of the recent rise of deep learning, in large part because of advances in methods for training networks, and advances in technology such as GPUs that allow for parallelized training. When benchmarked with scalar metrics like accuracy on computer vision tasks such as object recognition, these deep neural networks appear capable of human or super-human levels of skill. The first major gains in accuracy were seen on image classification tasks such as ImageNet <cite data-cite="6027200/WGZWMWX7"></cite>, and the deep neural networks that made these advances were built with what are known as convolutional layers. As the name implies, these layers perform a convolution-like operation by multiplying filters of learned weights with the input image, producing as outputs feature maps that can be further transformed by succeeding layers. Convolutional neural networks (CNNs) represent the state of the art in image recognition. Many mechanisms proposed to extend the abilities of CNNs have been given the name "attention", and these attention mechanisms typically involve some sort of recurrence [@baMultipleObjectRecognition2014; @mnihRecurrentModelsVisual2014; @xuShowAttendTell2015]. These mechanisms are arguably analogous to what is called **overt** attention in psychology and neuroscience. In the context of vision, overt attention describes movement of the eyes or head so that the high-acuity fovea is placed on the focus of attention. In contrast, **covert** attention is any mechanism that occurs internally to select features relevant for a task while discarding irrelevant features. Covert attention can be considered one type of **dynamic routing** of information thought to occur in the brain. Models of dynamic routing, inspired by studies of visual attention [@bobierAttentionalRoutingCircuit2011; @bobierUnifyingMechanisticModel2014a; @olshausenMultiscaleDynamicRouting1995; @olshausenNeurobiologicalModelVisual1993] have also formed the basis of attention-like mechanisms in applied research on neural networks [@tangLearningGenerativeModels2014]. The function of CNNs has not typically been considered within the context of this work on covert visual attention.

### Convolutional neural networks as models of the visual system
Recently, many in neuroscience and cognitive science have returned to using neural network models to understand the brain, in part because of their resurgence. More specifically, many researchers have drawn parallels between the architecture of CNNs and the architecture of the visual system in the brain <cite data-cite="6027200/8ISULWGF"></cite>, in particular in humans and other primates where this system has been most thoroughly studied. Like CNNs, the visual system has a hierarchical structure, and is thought to function in part by performing transformations at each level of this hierarchy so that high-dimensional, low-level features are mapped into low-dimensional abstract representations. Several recent studies in the realm of cognitive neuroscience have measured representations in more directly tested the similarities between CNNs and the visual system, by comparing representations in both <cite data-cite="6027200/6D4LKJD9"></cite><cite data-cite="6027200/U77Y74SI"></cite>. Representations can be easily extracted from CNNs because they are "transparent box" models--i.e. we have access to the "activity" of the individual units from which these models are built when we "show" the CNNs a stimulus. In the same studies, brain activity was obtained with electrophysiological or functional imaging methods. Such studies have found in general that representations are similar. (The comparison depends on representational similarity methods <cite data-cite="6027200/IQ2Y895S"></cite><cite data-cite="6027200/EQTU2P3Z"></cite>, but the concern of this study is not the validity of those methods.)

### Visual search tasks for investigating attention
In the "classical" form of the visual search paradigm [@wolfeVisualSearch1998], experimenters present a subject with a search display on which there are discrete items, i.e. objects. The subject is asked to report whether a target is present among distractors. The experimenter sets the probability that the target will be present on any given trial. Experimenters measure the reaction time and/or accuracy of the subjects. Often, the results are presented as a plot of reaction time as a function of set size (the number of discrete items in stimulus). By fitting a line to the plot of reaction times as a function of set size and taking the slope of that line, experimenters produced estimates of processing speed, i.e. "seconds per item". Slopes are almost horizontal when subjects are shown visual search stimuli where targets differ from distractors in some clearly salient **feature**, e.g. a red target among green distractors, and slopes become much steeper when targets differ from distractors in some harder-to-distinguish **spatial conjunction** of features, e.g., a digital 2 among digital 5s. Some examples of these stimuli are shown below, generated with https://github.com/NickleDave/searchstims.
